---
title: "545Final Project_ Phase1_Eric Mao"
author: "Bangyu(Eric) Mao"
date: "11/27/2016"
output: pdf_document
---
```{r}
library(ggplot2)
library(dplyr)
library(lubridate)
library(stringr)


Data = read.csv("Data.csv",header = T)
```

# 1. Distribution of requests, distribution departments referred to

## Create the date range for the dataset: 2015/11/01 - 2016/11/01

```{r}


Data$Date=str_extract_all(Data$CreatedDate,"[0-9]{4}[-][0-9]{2}[-][0-9]{2}")
Data$Date = ymd(Data$Date)

Data_1Y = Data%>%
  filter(Date>"2015-11-01" & Date< "2016-10-31")
```

## Distribution of requests by month

```{r}
Data_1Y$Created_Month = factor(Data_1Y$Created_Month,levels = levels(Data_1Y$Created_Month)[c(10,3,5,4,8,1,9,7,6,2,12,11)])

ggplot(Data_1Y,aes(Created_Month)) +
  geom_bar(fill="#1AB58A") +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Month") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 30, family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  


```

## Distribution of requests by Day_of_Week

```{r}
Data_1Y$Created_Day = factor(Data_1Y$Created_Day,levels = levels(Data_1Y$Created_Day)[c(2,6,7,5,1,3,4)])

ggplot(Data_1Y,aes(Created_Day)) +
  geom_bar(fill="#FFAD29") +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Day of Week") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```


## HeatMap of requests by Hour and Dayofweek

```{r}
Data1 = Data_1Y%>%
  group_by(Created_Day,Created_Hour)%>%
  summarise(Count=n())
  
ggplot(Data1,aes(Created_Day,factor(Created_Hour),fill=Count)) +
  geom_tile() +
  scale_fill_gradient(low="#1AB58A", high = "#FF2151") +
  xlab("Day of Week") +
  ylab("Hour") +
  ggtitle("Heat Map of Requests By Hour and Day_of_Week") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```

## Distribution of departments reffered to

```{r}

ggplot(Data_1Y,aes(Owner_Full)) +
  geom_bar(fill="#FFAD29") +
  xlab("Department") +
  ylab("") +
  ggtitle("Distribution of Departments reffered to") +
  theme_linedraw() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 20, h=1),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```

# 2.App vs call vs Self_Service referrals, service type question for each input channel

## Create the subset contains the RequestSource of App,call,Self-serice
```{r}
Data2 = Data_1Y%>%
  filter(RequestSource %in% c("Call","Mobile App","Self Service"))

```


## General distribution of requests through 3 major Request Sources

```{r}
ggplot(Data2,aes(RequestSource)) +
  geom_bar(fill="#1AB58A",) +
  xlab("Major Request Soucr") +
  ylab("") +
  ggtitle("Distribution of Requests by Major Request Source") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
```


## General distribution of Service Questions through 3 major Request Sources

```{r}
ggplot(Data2,aes(RequestType,fill=RequestType)) +
  geom_bar() +
  xlab("Major Request Source") +
  ylab("") +
  ggtitle("General distribution of Service Questions through 3 major Request Sources") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30, h=1, size=8),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +
  facet_grid(RequestSource~., scales = "free")
```

## Distribution of Request Source on Different Hour

```{r}
Data3 = Data_1Y%>%
  filter(RequestSource%in% c("Call","Mobile App","Self Service"))%>%
  group_by(Created_Hour,RequestSource)%>%
  summarise(Count=n())

ggplot(Data3,aes(factor(Created_Hour),Count,fill=RequestSource)) +
  geom_bar(stat = "identity") +
  xlab("Hour") +
  ylab("") +
  ggtitle("Distribution of Request Source on Different Hour") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +facet_grid(RequestSource~., scales = "free") +
  scale_fill_manual(labels=letters[1:3], values=c("#FF2151","#FF7729","#FFAD29"),guid=F) 
  

```


# 3. Geographic + Service Type breakdown

## Request Distributions on Geo
```{r}
Data4 = Data_1Y%>%
  filter(RequestSource %in% c("Call","Mobile App","Self Service"))
library(ggmap)
LA = qmap("Los Angeles", color = "bw", zoom=10)

qmap("Los Angeles", color="bw",zoom=12) +
  stat_density2d(data=Data4,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon") +
  scale_fill_gradient(low = "#1AB58A", high = "#FF7729") +
  facet_wrap(~Created_Day, nrow = 3) +
  theme(legend.position = "none")
  
```


## Request Source Distributions on Geo

```{r}
LA = qmap("Los Angeles", color = "bw", zoom=10)

qmap("Los Angeles", color = "bw", zoom=12)+
  stat_density2d(data=Data4,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon") +
  scale_fill_gradient(low = "#1AB58A", high = "#FF7729") +
  facet_wrap(~RequestSource, nrow = 3) +
  theme(legend.position = "none")
  

```

## Request Type Distributions on Geo

```{r}
table(RequestType)

Data5 = Data_1Y%>%
  filter(RequestType %in% c("Bulky Items","Dead Animal Removalp","Electronic Waste","Graffiti Removal","Illegal Dumping Pickup","Metal/Household Appliances","Homeless Encampment","Single Streetlight Issue"))

qmap("Los Angeles", color = "bw", zoom=12)+
  stat_density2d(data=Data5,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon") +
  scale_fill_gradient(low = "#1AB58A", high = "#FF7729") +
  facet_wrap(~RequestType, nrow = 3) +
  theme(legend.position = "none")

```



