---
title: "545Final Project_ Phase1_Eric Mao"
author: "Bangyu(Eric) Mao"
date: "11/27/2016"
output: pdf_document
---
```{r}
library(ggplot2)
library(dplyr)
library(lubridate)
library(stringr)


Data = read.csv("Data.csv",header = T)
```


### Merge Data -- Demographic
```{r}
demographic = read.csv("Demographic.csv")
demographic = demographic[,-1]
colnames(demographic) = c("ZipCode","Median_Age","Median Household Income","Percent_of_Occupied_Housing_Units","Percent_of_Male","Num_of_Households")

demographic$ZipCode = str_replace_all(demographic$ZipCode," ","")

Data_merged = merge(x=Data,y=demographic,by= "ZipCode",all.x= T)
Data_merged=Data_merged%>%
  arrange(CreatedDate)
Data_merged = Data_merged[,-2]


```


# 1. Distribution of requests, distribution departments referred to

## Create the date range for the dataset: 2015/11/01 - 2016/11/01

```{r}

Data_merged$Date=str_extract_all(Data_merged$CreatedDate,"[0-9]{4}[-][0-9]{2}[-][0-9]{2}")
Data_merged$Date = ymd(Data_merged$Date)

Data_1Y = Data_merged%>%
  filter(Date>"2015-11-01" & Date< "2016-10-31")
```

## Distribution of requests by month

```{r}
library(ggthemes)

Data_1Y$Created_Month = factor(Data_1Y$Created_Month,levels = levels(Data_1Y$Created_Month)[c(1,4,10,8,3,2,5,9,12,11,7,6)])

ggplot(Data_1Y,aes(Created_Month)) +
  geom_bar(aes(fill=Created_Month)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Month") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 30, family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +
  scale_fill_manual(values=c(rep("#2AB69D",4),rep("#FDC536",5),rep("#2AB69D",3)), guid=F)
  

```

## Distribution of requests by month(Only Call)

```{r}
Data_1Y%>%
  filter(RequestSource=="Call")%>%
ggplot(aes(Created_Month)) +
  geom_bar(aes(fill=Created_Month)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Month(Call)") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 30, family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +
  scale_fill_manual(values=c(rep("#2AB69D",4),rep("#E65848",5),rep("#2AB69D",3)), guid=F)
  
```





## Distribution of requests by Day_of_Week

```{r}
Data_1Y$Created_Day = factor(Data_1Y$Created_Day,levels = levels(Data_1Y$Created_Day)[c(2,6,7,5,1,3,4)])

ggplot(Data_1Y,aes(Created_Day)) +
  geom_bar(fill="#FFAD29") +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Day of Week") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```

## Distribution of requests by Day_of_Week on Different Request Sources

```{r}
Data_1Y%>%
  filter(RequestSource %in% c("Call","Mobile App","Self Service","Driver Self Report"))%>%
ggplot(aes(Created_Day,fill=RequestSource)) +
  geom_bar(aes(fill=RequestSource),position = "fill",alpha=0.8) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Day of Week(Major Request Sources)") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +
  scale_fill_manual(values = c("#0074D9","#2AB69D","#F5A503","#F2385A"))
```







## HeatMap of requests by Hour and Dayofweek

```{r}
Data1 = Data_1Y%>%
  group_by(Created_Day,Created_Hour)%>%
  summarise(Count=n())
  
ggplot(Data1,aes(Created_Day,factor(Created_Hour),fill=Count)) +
  geom_tile() +
  scale_fill_gradient(low="#2AB69D", high = "#F2385A") +
  xlab("Day of Week") +
  ylab("Hour") +
  ggtitle("Heat Map of Requests By Hour and Day_of_Week") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```

## Distribution of departments reffered to

```{r}
Data_1Y%>%
  group_by(Owner_Full)%>%
  summarise(count = n())%>%
  arrange(-count)%>%
ggplot(aes(reorder(Owner_Full,-count),count)) +
  geom_bar(fill="#FFAD29",stat = "identity") +
  xlab("Department") +
  ylab("") +
  ggtitle("Distribution of Departments reffered to") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 20, h=1),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
  
```


```{r}
Data_1Y%>%
  filter(Owner_Full=="Bureau of Sanitation")%>%
  group_by(AssignTo)%>%
  summarise(count = n())%>%
  filter(count>30000)%>%
  arrange(-count)%>%
ggplot(aes(reorder(AssignTo,-count),count)) +
  geom_bar(aes(fill=AssignTo),stat = "identity") +
  xlab("Department") +
  ylab("") +
  ggtitle("Distribution of Orgnization assigned to(Bureau of Sanitation)") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 20, h=1),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )+
  scale_fill_manual(values=c("#DF5A49","#FFAD29",rep("#DF5A49",2),rep("#FFAD29",2)),guid=F)
```




# 2.App vs call vs Self_Service referrals, service type question for each input channel

## Create the subset contains the RequestSource of App,call,Self-serice
```{r}
Data2 = Data_1Y%>%
  filter(RequestSource %in% c("Call","Mobile App","Self Service","Driver Self Report"))

```


## General distribution of requests through 4 major Request Sources

```{r}
ggplot(Data2,aes(RequestSource)) +
  geom_bar(aes(fill=RequestSource)) +
  xlab("") +
  ylab("") +
  ggtitle("Distribution of Requests by Major Request Source") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )+
  scale_fill_manual(values = c("#DF5A49",rep("#1AB58A",3)),guid=F)
  
```


## General distribution of Service Questions through 3 major Request Sources

```{r}
Data2%>%
  filter(RequestSource%in%(c("Call","Mobile App","Self Service")))%>%
ggplot(aes(RequestType,fill=RequestType)) +
  geom_bar() +
  xlab("Major Request Source") +
  ylab("") +
  ggtitle("General distribution of Service Questions") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30, h=1, size=8),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +
  facet_grid(RequestSource~., scales = "free") 
```

## Distribution of Request Source on Different Hour

```{r}
Data3 = Data_1Y%>%
  filter(RequestSource%in% c("Call","Mobile App","Self Service"))%>%
  group_by(Created_Hour,RequestSource)%>%
  summarise(Count=n())

ggplot(Data3,aes(factor(Created_Hour),Count,fill=RequestSource)) +
  geom_bar(stat = "identity") +
  xlab("Hour") +
  ylab("") +
  ggtitle("Distribution of Request Source on Different Hour") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica"),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  ) +facet_grid(RequestSource~., scales = "free") +
  scale_fill_manual(labels=letters[1:3], values=c("#FF2151","#FF7729","#1AB58A"),guid=F) 
  

```


```{r}


```





# 3. Geographic + Service Type breakdown

## Request Distributions on Geo

```{r}
library(ggmap)
LA = qmap("Los Angeles", color = "bw", zoom=10)

LA+
  geom_point(data=Data_1Y,aes(Longitude,Latitude),alpha=1/500,color="#DF5A49") 
 
```


```{r}
Data4 = Data_1Y%>%
  filter(RequestSource %in% c("Call","Mobile App","Self Service"))
library(ggmap)

LA = qmap("Los Angeles", color = "bw", zoom=10)

Data5=Data_1Y%>%
  mutate(Weekday=ifelse(Created_Day %in% c("Mon","Tues","Wed","Thurs","Fri"),"Weekday","Weekend"))


  qmap("Los Angeles", color="bw",zoom=12) +
  stat_density2d(data=Data5,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon") +
    facet_wrap(~Weekday,nrow=1)+
  scale_fill_gradient(low = "#1AB58A", high = "#DF5A49") +
  theme(legend.position = "none")
  
```


## Request Source Distributions on Geo

```{r}
LA = qmap("Los Angeles", color = "bw", zoom=10)

qmap("Los Angeles", color = "bw", zoom=12)+
  stat_density2d(data=Data4,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon") +
  scale_fill_gradient(low = "#1AB58A", high = "#FF7729") +
  facet_wrap(~RequestSource, nrow = 2) +
  theme(legend.position = "none")
  

```

## Request Type Distributions on Geo

```{r}
table(RequestType)

Data5 = Data_1Y%>%
  filter(RequestType %in% c("Bulky Items","Graffiti Removal"))

qmap("Los Angeles",zoom=12,extent = "device",color="bw")+
  stat_density2d(data=Data5,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon",bins=4) +
scale_fill_gradient(low = "#942193",high = "#E65848") +
  facet_wrap(~RequestType, nrow = 1) +
  theme(legend.position = "none")

```

```{r}
#DTLA
Data_1Y$Created_Day = factor(Data_1Y$Created_Day,levels = levels(Data_1Y$Created_Day)[c(2,6,7,5,1,3,4)])

Data_1Y%>%
  filter(ZipCode%in% c("90012","90013","90014","90074","90017","90071","90081","90053","90015","90021","90079","90055","90021","90086"))%>%
  group_by(Created_Day,Created_Hour)%>%
  summarise(Count=n())%>%
ggplot(aes(Created_Day,factor(Created_Hour),fill=Count)) +
  geom_tile() +
  scale_fill_gradient(low="#2AB69D", high = "#E27A3F") +
  xlab("Day of Week") +
  ylab("Hour") +
  ggtitle("Heat Map of Requests By Hour and Day_of_Week in DTLA") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
```


```{r}
Data_1Y%>%
  filter(ZipCode%in% c("90019"))%>%
  group_by(Created_Day,Created_Hour)%>%
  summarise(Count=n())%>%
ggplot(aes(Created_Day,factor(Created_Hour),fill=Count)) +
  geom_tile() +
  scale_fill_gradient(low="#2AB69D", high = "#E27A3F") +
  xlab("Day of Week") +
  ylab("Hour") +
  ggtitle("Heat Map of Requests By Hour and Day_of_Week in DTLA") +
  theme_classic() +
  theme(
    axis.text.x = element_text(family="Helvetica",angle = 30),
    axis.text.y = element_text(family="Helvetica"),
    plot.title = element_text(face="bold",color="darkgrey")
  )
  
```


### Water and Electricity by ZipCode

```{r}
Data6 = Data_1Y%>%
  filter(RequestType=="Report Water Waste")%>%
  group_by(ZipCode)%>%
  summarise(ele_request = n())
Data6 = Data6[-c(1,2),]


WE = read.csv("Water_And_Electric.csv",header = T)

Data6_2 = merge(Data6,WE,by="ZipCode",all.x=T)


ggplot(Data6_2,aes(WaterUse,ele_request)) +
  geom_point() +
 xlim(0,200) +
 ylim(0,50)
```


```{r}
Data5 = Data_1Y%>%
  filter(RequestType %in% c("Bulky Items","Graffiti Removal","Homeless Encampment","Single Streetlight Issue"))%>%
  filter(Owner_Full%in%c("Bureau of Sanitation","Office of Community Beautification"))

ggplot(Data5,aes(Owner_Full,fill=RequestType)) +
  geom_bar(position = "fill")




```



```{r}
Data_V=Data_1Y%>%
  filter(Owner_Full%in%c("Bureau of Sanitation","Office of Community Beautification"))%>%
  group_by(Owner_Full,AssignTo)%>%
  summarise(Count=n())
table(Data_V$Owner_Full,Data_V$AssignTo)
```


```{r}
Data7 = Data_1Y%>%
  filter(RequestSource%in% c("Call","Mobile App","Self Service","Driver Self Report"))%>%
  filter(Owner_Full=="Office of Community Beautification")%>%
  mutate(SD= ifelse(RequestSource=="Driver Self Report","Driver","Self"))%>%
  mutate(Weekday=ifelse(Created_Day%in%c("Sun","Sat"),"Weekend","Weekday"))


Data7_1 = Data7%>%
  filter(Weekday =="Weekend" & SD=="Driver")
qmap("Los Angeles", zoom=12, color="bw") +
  stat_density2d(data=Data7_1,aes(Longitude,Latitude,fill=..level..,alpha=..level..),
                 geom ="polygon") +
  scale_fill_manual(values = c("#FDC536","#E65848"))+
  theme(
    legend.position="none"
  ) 



```


```{r}
Data8 = Data_1Y%>%
  filter(RequestType %in% c("Bulky Items"))

qmap("Los Angeles",zoom=12,extent = "device",color="bw")+
  stat_density2d(data=Data8,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon",bins=4) +
scale_fill_gradient(low = "#942193",high = "#E65848") +
  facet_wrap(~RequestType, nrow = 1) +
  theme(legend.position = "none") +
  facet_wrap(~Created_Day,nrow = 3)
```

```{r}
Data9 = Data_1Y%>%
  filter(RequestType %in% c("Graffiti Removal"))

qmap("Los Angeles",zoom=12,extent = "device",color="bw")+
  stat_density2d(data=Data9,aes(Longitude,Latitude,fill=..level..,alpha=..level..),geom="polygon",bins=4) +
scale_fill_gradient(low = "#FCF2D7",high = "#E65848") +
  facet_wrap(~RequestType, nrow = 1) +
  theme(legend.position = "none") +
  facet_wrap(~Created_Day,nrow = 3)
```



```{r}
Data10 = Data_1Y%>%
  filter(ZipCode%in%c("90010","90020","90005","90007"))%>%
    filter(RequestType %in% c("Bulky Items","Graffiti Removal"))

qmap("Los Angeles Koreatown",zoom=15,extent = "device",color="bw")+
  geom_point(data=Data10,aes(Longitude,Latitude,color=RequestType),alpha=0.5) 

```




